Broom: Safe Region-Based Memory Management for Dataflow Programs

### 2015-10-27 paper/broom.tex
Text added to Sec.3
The type system ensures complete memory safety.
Edits.
Reduced rules to use in main paper.
Text on static semantics.
Sec 3 complete.
Major simplification of type rules.
Simplifications applied from techrep to master.
Sec 3. complete.
Type inference first commit.

@@

@@

\newcommand{\headerOf}[1]{\C{class}\; #1\angR\angAlpha \extends \fbN}

@@

\newcommand{\rhoset}{\Sigma}

@@

\newcommand{\subtypcx}{\rhoset,\rhoenv,\aenv,\phicx}

@@

\newcommand{\okin}[2]{#1 \; \texttt{ok \; in} \; #2}
\newcommand{\lambdaexp}[3]{\lambda\inang{#1}(#2).#3}

@@

\newcommand{\open}[3]{\C{open}\;#1\;\C{withroot}\;#2\;\C{in}\;#3}

@@

@@

\newcommand{\lstjava}{\lstset{ %
language=Java, % choose the language of the code
basicstyle=\small\ttfamily,       % the size of the fonts that are used for the code
keywordstyle=\color{Bittersweet},
% numbers=left,                   % where to put the line-numbers
numberstyle=\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
% frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
commentstyle=\itshape\color{MidnightBlue},
%escapeinside={\%*}{*)},         % if you want to add a comment within your code
morekeywords={letregion, openalloc, open, withroot, not, : , /\\}
}}
\lstnewenvironment{codejava}
    { % \centering
			\lstjava
      \lstset{}%
      \csname lst@setfirstlabel\endcsname}
    { %\centering
      \csname lst@savefirstlabel\endcsname}

@@

@@

>>>>

\newcommand{\eqtyp}[3]{#1\,\vdash\,#2 \equiv #3}

@@

\newcommand{\underlives}{\preceq}

@@

\newcommand{\headerOf}[1]{\C{class}\; #1\angAlpha\angR \extends \fbN}

@@

\newcommand{\rhoset}{\rhoenv}

@@

\newcommand{\subtypcx}{\rhoenv,\aenv,\phicx}

@@

\newcommand{\okin}[2]{#1 \; \texttt{ok} \; \texttt{in} \; #2}
\newcommand{\lambdaexp}[3]{\lambda\inang{#1}(#2). #3}

@@

\newcommand{\open}[4]{\C{open}\;#1\;\C{as}\;#2\;\C{withroot}\;#3\;\C{in}\;#4}

@@

\newcommand{\invalidexn}{\C{InvalidOpnException}}
\newcommand{\toprgn}{\rgn_{\top}}
\newcommand{\csolvestar}{{\sc CSolve*}\xspace}
\newcommand{\elabExpr}{{\sf elabExpr}}
\newcommand{\fields}{{\sf fields}}
\newcommand{\mtype}{{\sf mtype}}
\newcommand{\bound}{{\sf bound}}
\newcommand{\fresh}{{\sf fresh}}
\newcommand{\typeOk}{{\sf typeOk}}
\newcommand{\subtypeOk}{{\sf subtypeOk}}
\newcommand{\templateTy}{{\sf templateTy}}
\newcommand{\allocRgn}{{\sf allocRgn}}
%\newcommand{\smallskip}{\vspace*{0.1in}}

@@

\newcommand{\lstjava}{\lstset{ %
language=Java, % choose the language of the code
basicstyle=\small\ttfamily,       % the size of the fonts that are used for the code
keywordstyle=\color{Bittersweet},
% numbers=left,                   % where to put the line-numbers
numberstyle=\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
% frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
commentstyle=\itshape\color{MidnightBlue},
%escapeinside={\%*}{*)},         % if you want to add a comment within your code
morekeywords={letregion, let, in, as, openalloc, open, withroot, not, : , /\\}
}}
\lstnewenvironment{codejava}
    { % \centering
			\lstjava
      \lstset{mathescape=true}%
      \csname lst@setfirstlabel\endcsname}
    { %\centering
      \csname lst@savefirstlabel\endcsname}

@@

\newcommand{\lstml}{\lstset{ %
language=[Objective]Caml, % choose the language of the code
basicstyle=\small\ttfamily,       % the size of the fonts that are used for the code
keywordstyle=\color{Bittersweet},
% numbers=left,                   % where to put the line-numbers
numberstyle=\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
% frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
commentstyle=\itshape\color{MidnightBlue},
escapeinside={\%*}{*)},         % if you want to add a comment within your code
morekeywords={relation, not, : , /\\}
}}
\lstnewenvironment{codeml}
    { % \centering
			\lstml
      \lstset{mathescape=true}%
      \csname lst@setfirstlabel\endcsname}
    { %\centering
      \csname lst@savefirstlabel\endcsname}

@@

\input{type-inference}
